Fractional Types

### 2019-11-23 fracGC/p.tex
Minor typos

%%%
\subsection{Ancillae Bugs in Benchmarks.}
Despite its fundamental importance, the management of ancillae is
poorly supported in current languages, simulators, and toolkits.
A recent analysis of bugs in quantum
benchmarks~\cite{DBLP:conf/oopsla/HuangM18} demonstrates this. The analysis
reveals that lack of language support in the management of ancillae leads to
several problems. For example:
\begin{quote}
  \textbf{Bug type 6: Incorrect composition of operations using mirroring}
  Section~4.5 discussed how bugs in deallocating ancillary qubits can
  happen due to bad parameters. Here we see how bugs in deallocating
  ancillary qubits can happen due to incorrect composition of
  operations following a mirroring pattern. For example, in Table~7,
  the operations in rows 2 and 3 are respectively mirrored and undone
  in rows~6 and~5. These lines of code need careful reversal of every
  loop and every operation.
\end{quote}

@@

Proceeding similarly, we create a
version of $\Pi$ with pointed types which we call
$\Pi/\bullet$. In addition to the pointed types of the form
$t$\Acon{\#}$v$, we need a multiplicative structure over pointed
types, fractional types, and a special kind of pointed type that
includes just one value, a singleton type. The singleton types will
allow the type system to track the flow of one particular value, which
is exactly what is needed to prove the safety of deallocation:

>>>>

%%%
\subsection{Ancillae Bugs in Benchmarks.}
Despite its fundamental importance, the management of ancillae is
poorly supported in current languages, simulators, and toolkits.
A recent analysis of bugs in quantum
benchmarks~\cite{DBLP:conf/oopsla/HuangM18} demonstrates this. The analysis
reveals that lack of language support in the management of ancillae leads to
several problems. For example:
\begin{quote}
  \textbf{Bug type 6: Incorrect composition of operations using mirroring}
  Section~4.5 discussed how bugs in de-allocating ancillary qubits can
  happen due to bad parameters. Here we see how bugs in de-allocating
  ancillary qubits can happen due to incorrect composition of
  operations following a mirroring pattern. For example, in Table~7,
  the operations in rows 2 and 3 are respectively mirrored and undone
  in rows~6 and~5. These lines of code need careful reversal of every
  loop and every operation.
\end{quote}

@@

Proceeding similarly, we create a
version of $\Pi$ with pointed types which we call
$\Pi/\bullet$. In addition to the pointed types of the form
$t$\Acon{\#}$v$, we need a multiplicative structure over pointed
types, fractional types, and a special kind of pointed type that
includes just one value, a singleton type. The singleton types will
allow the type system to track the flow of one particular value, which
is exactly what is needed to prove the safety of de-allocation:
